full title

### 2020-11-20 paper/pldi21/implementation.tex
Revised Sec. 5

\section{Implementation}\label{sec:implementation}

We have implemented the dynamic shortcut for JavaScript static analysis
presented in Section~\ref{sec:javascript} in a prototype implementation called
$\tool$.  The tool is an extension of an existing state-of-the-art JavaScript
static analyzer SAFE~\cite{safe, safe2} with a dynamic analyzer
Jalangi~\cite{jalangi}, and it is open source and available online~\footnote{The
URL of the tool is anonymized due to a double-blind review process.}.  In this
section, we introduce challenges and solutions when implementing dynamic
shortcut on existing JavaScript analyzers.

\paragraph{Sealed Symbolic Values.}
The main challenge of implementing dynamic shortcut is to support the sealed
symbolic execution on the existing JavaScript engine.  To represent an abstract
value, we leverage the \jscode{Proxy} object introduced in ECMAScript 6
(2015, ES6)~\cite{es6}, which allows developers to handle the internal behaviors
of specific objects (such as property reads and writes, implicit conversions,
etc.).  We are inspired by \textsc{Mimic}~\cite{mimic} using \jscode{Proxy} to
capture accesses from the inside of opaque functions.  When the dynamic analyzer
constructs the execution environments at the start of the dynamic shortcut, it
creates revoked \jscode{Proxy} objects to represent each abstract values via the
following \jscode{generateSymbol} function:
\begin{lstlisting}[style=myJSstyle]
function generateSymbol() {
  const r = Proxy.revocable(function() {}, {});
  r.revoke();
  return r.proxy;
}
var x = generateSymbol();
var y = x;
var z = x + 1;
\end{lstlisting}
The function creates a sealed symbol as a revocable proxy object with a dummy
function object without any handlers and revokes it by
\jscode{revocable.revoke()} to not allow any access of the symbol.  The revoked
object throws a \jscode{TypeError} when the object faces 13 kinds of operations
so we can determine whether or not the seal is open.  For example, the variable
\jscode{y} successfully points to the same symbol stored in \jscode{x} but the
program throws the \jscode{TypeError} in line 8 because \jscode{x + 1} requires
the actual value of the symbol.  Moreover, we instrument unary and binary
operations on Jalangi to fully cover accesses on the symbol beyond 13 traps
provided by \jscode{Proxy}.  Using this idea, we successfully extend the
JavaScript engine to support a sealed symbolic execution.

\paragraph{Synchronization of Control Points.}
For seamless interactions between the static analyzer and dynamic shortcuts,
the synchronization of control points is a prerequisite.
The static analyzer compiles a target JavaScript program to intermediate
representation and builds a control flow graph.  It produces annotations for
control points on the CFG including functions, call sites, and object allocation
sites.  During the sealed symbolic execution, the dynamic analyzer requires
those annotations to calculate sensitive location names of newly created object
and lexical environments.  The key to place annotations on the instrumented code
is the span information of the original AST node.  Both the CFG of SAFE and
instrumented code of Jalangi maintain the span information, but they use
different parsers resulting mismatches for some corner cases.  Thus, we
preprocess to synchronize control points of two analyzers by the closest match
of the span information rather than the exact match.

\paragraph{Optimizations.}
To perform dynamic shortcut, the static analyzer should communicate with the
dynamic analyzer by passing the current abstract state and receiving the final
result of the sealed symbolic execution.  When abstract states are massive, it
is burden to send them as they stand.  Thus, we perform mark-and-sweep garbage
collection to remove unreachable information in the current abstract state.
Moreover, the abstract values are converted to the sealed symbolic values and
their contents are not necessary in the dynamic analysis.  Thus, we replace
abstract values with their unique identifiers and stores the table from
identifiers to abstract values before sending the abstract state
from the static analyzer.  Thus, the dynamic analyzer only receives identifiers
of abstract values and wrap them as \jscode{Proxy} objects.  After finishing the
sealed symbolic execution, the static analyzer recovers the abstract values in
the result abstract state using the table.

\paragraph{Termination.}
To guarantee the termination of static analysis with dynamic shortcut, the
filter $\checker$ should pass the state $\symbst$ only when it terminates in a
bound time $N$.  Since it is difficult to statically check its termination,
we just performs the sealed symbolic execution with a time limit.  When it runs
over the time limit, we treat it fails to pass $\checker$, otherwise we utilizes
the result of the execution.  In the experiments, we set the time limit as
\inred{5 seconds} for each sealed symbolic execution.

>>>>

\section{Implementation}\label{sec:implementation}
We implemented JavaScript static analysis using dynamic shortcuts
presented in Section~\ref{sec:javascript} in a prototype implementation dubbed
$\tool$.  The tool is an extension of an existing state-of-the-art JavaScript
static analyzer SAFE~\cite{safe, safe2} with a dynamic analyzer
Jalangi~\cite{jalangi}, and it is an open-source project and available online~\footnote{The
URL of the tool is anonymized due to a double-blind review process.}.  In this
section, we introduce challenges and solutions in implementing dynamic
shortcuts on existing JavaScript analyzers.

\paragraph{Sealed Symbolic Values.}
The main challenge of implementing dynamic shortcuts is to support sealed
symbolic execution on an existing JavaScript engine.  To represent an abstract
value, we leverage the \jscode{Proxy} object introduced in ECMAScript 6
(2015, ES6)~\cite{es6}, which allows developers to handle internal behaviors
of specific objects such as property reads and writes and implicit conversions.
We are inspired by \textsc{Mimic}~\cite{mimic}, which used \jscode{Proxy} to
capture accesses from internals of opaque functions.  When the dynamic analyzer
constructs an execution environment at the start of a dynamic shortcut, it
creates revoked \jscode{Proxy} objects to represent abstract values via the
following \jscode{generateSymbol} function:
\begin{lstlisting}[style=myJSstyle]
function generateSymbol() {
  const r = Proxy.revocable(function() {}, {});
  r.revoke();
  return r.proxy;
}
var x = generateSymbol();
var y = x;
var z = x + 1;
\end{lstlisting}
The function creates a sealed symbol \jscode{r} as a revocable proxy object with a dummy
function object without any handlers. It then revokes the symbol by
\jscode{r.revoke()} not to allow any accesses of the symbol.  A revoked
object throws a \jscode{TypeError} exception when any of 13 pre-defined operations
are applied to the object, which enables us to determine whether an
object is sealed or not.  For example, the variable
\jscode{y} successfully points to the same symbol stored in \jscode{x}, but the
program throws \jscode{TypeError} on line 8 because \jscode{x + 1} requires
the actual value of the symbol.  In addition, we instrument unary and binary
operations in Jalangi so that we can detect all the accesses on the
symbol beyond the 13 operations provided by \jscode{Proxy}.
Using this idea, we successfully extended the
JavaScript engine to support sealed symbolic execution.

\paragraph{Synchronization of Control Points.}
For seamless interaction between static analysis and sealed symbolic execution,
synchronization of control points in both worlds is a prerequisite.
The SAFE static analyzer parses a JavaScript program to an Abstract
Syntax Tree (AST), compiles it to its intermediate representation, and
builds a Control Flow Graph (CFG).  It produces annotations for
control points on the CFG including functions, call sites, and object allocation sites.
On the contrary, the Jalangi dynamic analyzer instruments a JavaScript program 
to keep track of necessary information at run time.  Therefore, during
sealed symbolic execution, Jalangi requires the annotations from SAFE to compute
abstract locations of newly created concrete objects and lexical environments.
The key to put annotations on the instrumented code is the source-code
location of the original AST node.  While both CFG of SAFE and
instrumented code of Jalangi maintain the source-code location information,
because they use different parsers we found various location mismatches for corner cases.
Therefore, we synchronize control points of two analyzers by using the closest match
of their source-code locations rather than using their exact match.

\paragraph{Optimizations.}
To use dynamic shortcuts, the static analyzer should communicate with the
dynamic analyzer by passing abstract states and receiving results of sealed
symbolic execution.  When abstract states are massive, sending
abstract states and receiving sealed symbolic values as they are could
incur large performance overhead.  Thus, we
implemented mark-and-sweep garbage collection to remove unreachable
information in abstract states.  In addition, because abstract values
themselves are not used in sealed symbolic execution, we make a map
from unique identifiers to abstract values and replace
abstract values with their unique identifiers when we convert abstract
values to sealed symbolic values.  Therefore, the dynamic analyzer
receives only identifiers of abstract values and wraps them as
\jscode{Proxy} objects.  After finishing sealed symbolic execution,
the static analyzer recovers the abstract values in the results of
sealed symbolic execution by replacing unique identifiers with their
corresponding abstract values.

\paragraph{Termination.}
To guarantee the termination of static analysis using dynamic shortcuts, the
filter $\checker$ should pass a state $\symbst$ only when it terminates in a
bound time $N$.  Since statically checking the termination property is a difficult task,
we simply perform sealed symbolic execution with a pre-determined time limit.  When it runs
over the time limit, we treat it as a failure to pass $\checker$; otherwise, we utilize
the result of the sealed symbolic execution.  In our experiments, we set the time limit as
\inred{5 seconds} for each sealed symbolic execution.

### 2020-11-20 paper/pldi21/shortcut.tex
Revised Sec. 5

For example, the code in Figure~\ref{fig:running-example} is a simple program
that applies the mathematical absolute value function to the variable $\varx$.
The question mark $?$ denotes the user input that returns an integer.  States
are pairs of labels and integers $\varx$: $\stset = \labset \times \mathbb{N}$.
The initial states are $\istset = \{ (\lab_0, 0) \}$ which means the program
starts with the variable $\varx$ that stores 0 at $\lab_0$.  If the user input is
$-42$, the program is executed with the following trace:
\[
  (\lab_0, 0) \trans (\lab_1, -42) \trans (\lab_3, -42) \trans (\lab_4, 42)
\]

@@

One of the most widely-used analysis sensitivity is \textit{flow sensitivity}
defined with the flow-sensitive view abstraction $\fsviewmap: \labset
\rightarrow \dom$ where
\[
  \forall \lab\in\labset. \; \fsviewmap(\lab) = \{ \st \mid \st = (\lab, \_) \}
\]
If we apply the flow sensitivity for the above example, the analysis result
becomes as follows:
\[
  \begin{array}{|c||c|c|c|c|c|}\hline
    \labset & \lab_0 & \lab_1 & \lab_2 & \lab_3 & \lab_4\\\hline
    \absdom_\pm & 0 & -, +, 0 & +, 0 & - & +, 0\\\hline
  \end{array}
\]

@@

To handle abstract values in concrete semantics, we define \textit{sealed
symbolic execution} by extending the transition relation $\trans$ as a symbolic
transition relation $\symbtrans$ on symbolic states.  First, we extends the
concrete states $\stset$ to symbolic states with \textit{sealed symbolic values}
$\symbset$.  A symbolic transition relation $\symbtrans \subseteq \symbstset
\times (\symbstset \uplus \{ \excst \})$ is exactly the same with the original
transition relation $\trans$ except when the relation requires the exact value
of sealed symbolic values.  In this case, the symbolic state has the relation a
special exception state $\excst$ to represent that it is impossible to interpret
in a concrete way.  Thus, a symbolic state \textit{always} has a symbolic
transition relation with a single symbolic state, and the sealed symbolic
execution is linear until being terminated or reaching the exception state
$\excst$.

>>>>

For example, the code in Figure~\ref{fig:running-example} is a simple program
that applies the mathematical absolute value function to the variable $\varx$.
The question mark $?$ denotes a user input that returns an integer.  States
are pairs of labels and integers $\varx$: $\stset = \labset \times \mathbb{N}$.
The initial states are $\istset = \{ (\lab_0, 0) \}$ which means the program
starts with the variable $\varx$ that stores 0 at $\lab_0$.  If the user input is
$-42$, the program is executed with the following trace:
\[
  (\lab_0, 0) \trans (\lab_1, -42) \trans (\lab_3, -42) \trans (\lab_4, 42)
\]

@@

One of the most widely-used analysis sensitivity is \textit{flow sensitivity}
defined with the flow-sensitive view abstraction $\fsviewmap: \labset
\rightarrow \dom$ where:
\[
  \forall \lab\in\labset. \; \fsviewmap(\lab) = \{ \st \mid \st = (\lab, \_) \}
\]
If we apply the flow sensitivity for the above example, the analysis result
becomes as follows:
\[
  \begin{array}{|c||c|c|c|c|c|}\hline
    \labset & \lab_0 & \lab_1 & \lab_2 & \lab_3 & \lab_4\\\hline
    \absdom_\pm & 0 & -, +, 0 & +, 0 & - & +, 0\\\hline
  \end{array}
\]

@@

To handle abstract values in concrete semantics, we define \textit{sealed
symbolic execution} by extending the transition relation $\trans$ as a symbolic
transition relation $\symbtrans$ on symbolic states.  First, we extend the
concrete states $\stset$ to symbolic states with \textit{sealed symbolic values}
$\symbset$.  A symbolic transition relation $\symbtrans \subseteq \symbstset
\times (\symbstset \uplus \{ \excst \})$ is exactly the same with the original
transition relation $\trans$ except when the relation requires the exact value
of sealed symbolic values.  In this case, the symbolic state has the relation a
special exception state $\excst$ to represent that it is impossible to interpret
in a concrete way.  Thus, a symbolic state \textit{always} has a symbolic
transition relation with a single symbolic state, and the sealed symbolic
execution is linear until being terminated or reaching the exception state
$\excst$.
